### 2017-11-03 submission/manuscript.Rmd
add data table

loadLibs(c("tidyverse", "scales", "knitr", "rmarkdown"))

@@

@@

@@

@@

>>>>

loadLibs(c("tidyverse", "scales", "knitr", "rmarkdown", "stringr"))

@@

#Read in meta data files used
studies <- c("Ahn", "Baxter", "Brim", "Burns", "Chen", "Dejea", "Flemer", "Geng", "Hale", "Lu", "Sana", "Wang", "Weir", "Zeller")

study_metadata <- sapply(studies, function(x) 
  read_tsv(paste("../data/process/", str_to_lower(x), "/", str_to_lower(x), ".metadata", sep = "")), simplify = F)

@@

\footnotesize

@@

sample_type <- c("Stool", "Stool", "Stool", "Tissue", "Stool + Tissue", "Tissue", "Stool + Tissue", "Tissue", "Stool", "Tissue", "Tissue", "Stool", "Stool", "Stool")

individuals <- c("control, carcinoma", "control, adenoma, carcinoma", "control, adenoma", "carcinoma", "control, carcinoma", "adenoma, carcinoma", "control, adenoma, carcinoma", "carcinoma", "control, adenoma, carcinoma", "control, adenoma", "control, carcinoma", "control, carcinoma", "control, carcinoma", "control, adenoma, carcinoma")

data_obtained <- c("DBGap", "SRA", "SRA", "SRA", "SRA", "SRA", "Author", "SRA", "Author", "SRA", "Author", 
                   "SRA", "Author", "SRA")

final_n <- c(length(unique(study_metadata[["Ahn"]]$sample)), length(unique(study_metadata[["Baxter"]]$sample)), length(unique(study_metadata[["Brim"]]$sample)), length(rownames(filter(study_metadata[["Burns"]], disease == "cancer"))), length(rownames(filter(study_metadata[["Chen"]], sample_type != "swab"))), length(unique(study_metadata[["Dejea"]]$patient_id)), length(unique(study_metadata[["Flemer"]]$sample)), length(rownames(filter(study_metadata[["Geng"]], disease == "cancer"))), length(unique(study_metadata[["Hale"]]$sample)), round((length(rownames(filter(study_metadata[["Lu"]], disease == "control"))) - length(rownames(filter(study_metadata[["Lu"]], disease == "polyp"))))/2) + length(rownames(filter(study_metadata[["Lu"]], matched == "n"))) + length(rownames(filter(study_metadata[["Lu"]], disease == "polyp"))) + 1, length(unique(study_metadata[["Sana"]]$sample)), length(unique(study_metadata[["Wang"]]$sample)), length(unique(study_metadata[["Weir"]]$sample)), length(unique(study_metadata[["Zeller"]]$sample)))

table1 <- cbind(studies, sample_type, individuals, data_obtained, final_n)

colnames(table1) <- c("Study", "Sample Type", "Individuals", "Data Stored", "mothur Processed n")

@@

\normalsize
\newpage

### 2017-11-03 submission/manuscript.tex
add data table

\begin{longtable}[]{@{}cccc@{}}
\toprule
country & year & cases & population\tabularnewline
\midrule
\endhead
Afghanistan & 1999 & 745 & 19987071\tabularnewline
Afghanistan & 2000 & 2666 & 20595360\tabularnewline
Brazil & 1999 & 37737 & 172006362\tabularnewline
Brazil & 2000 & 80488 & 174504898\tabularnewline
China & 1999 & 212258 & 1272915272\tabularnewline
China & 2000 & 213766 & 1280428583\tabularnewline
\bottomrule
\end{longtable}

>>>>

\footnotesize

\begin{longtable}[]{@{}ccccc@{}}
\toprule
Study & Sample Type & Individuals & Data Stored & mothur Processed
n\tabularnewline
\midrule
\endhead
Ahn & Stool & control, carcinoma & DBGap & 240\tabularnewline
Baxter & Stool & control, adenoma, carcinoma & SRA & 490\tabularnewline
Brim & Stool & control, adenoma & SRA & 12\tabularnewline
Burns & Tissue & carcinoma & SRA & 43\tabularnewline
Chen & Stool + Tissue & control, carcinoma & SRA & 100\tabularnewline
Dejea & Tissue & adenoma, carcinoma & SRA & 25\tabularnewline
Flemer & Stool + Tissue & control, adenoma, carcinoma & Author &
314\tabularnewline
Geng & Tissue & carcinoma & SRA & 8\tabularnewline
Hale & Stool & control, adenoma, carcinoma & Author & 770\tabularnewline
Lu & Tissue & control, adenoma & SRA & 67\tabularnewline
Sanapareddy & Tissue & control, carcinoma & Author & 71\tabularnewline
Wang & Stool & control, carcinoma & SRA & 102\tabularnewline
Weir & Stool & control, carcinoma & Author & 15\tabularnewline
Zeller & Stool & control, adenoma, carcinoma & SRA & 224\tabularnewline
\bottomrule
\end{longtable}

\normalsize
\newpage
